---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mytablepkg

<!-- badges: start -->
[![R-CMD-check](https://github.com/melindahiggins2000/mytablepkg/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/melindahiggins2000/mytablepkg/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/melindahiggins2000/mytablepkg/graph/badge.svg)](https://app.codecov.io/gh/melindahiggins2000/mytablepkg)
<!-- badges: end -->

The goal of `mytablepkg` is to make tables easier from the `gtsummary::tbl_summary()` functions. Add more here.

## Installation

You can install the development version of mytablepkg from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("melindahiggins2000/mytablepkg")
```

## Example with `palmerpenguins` package data

This is a basic example which shows you how to get a table for normally distributed continuous variables showing the mean and standard deviation.

```{r example, message = FALSE, warning = FALSE}
library(mytablepkg)
library(palmerpenguins)
mytablepkg::cont_table(
  c("bill_length_mm", "body_mass_g"),
  penguins
)
```


